DSIA: Data Systems for Interactive Analysis

### 2017-02-22 2017/paper.tex
tiny typo

The first DSIA workshop was held in VIS 2015 with somewhere around 150 to 200 attendees. 
We were able to bring in young, but prominent researchers in Databases, including Eugene Wu (Columbia), Arnab Nandi (Ohio State), Aditya Parameswaran (Illinois), Aaron Elmore (Univ of Chicago), Jenny Duggan (Northwestern), Leilani Battle (MIT); as well as senior researchers like Marti Hearst (Berkeley) and Joe Hellerstein (Berkeley, who was also the invited keynote speaker). 
Overall, the event was successful -- we observed the researchers from both sides interacting with each other, and anecdotally we are aware of a few collaborative projects borne from these discussions. 
For example, the collaboration between Jean-Daniel Fekete and Tim Kraska (Brown University) resulted in a recent TVCG paper~\cite{zgraggen2016progressive}.

>>>>

The first DSIA workshop was held in VIS 2015 with somewhere around 150 to 200 attendees. 
We were able to bring in young, but prominent researchers in Databases, including Eugene Wu (Columbia), Arnab Nandi (Ohio State), Aditya Parameswaran (Illinois), Aaron Elmore (Univ. of Chicago), Jenny Duggan (Northwestern), Leilani Battle (MIT); as well as senior researchers like Marti Hearst (Berkeley) and Joe Hellerstein (Berkeley, who was also the invited keynote speaker). 
Overall, the event was successful -- we observed the researchers from both sides interacting with each other, and anecdotally we are aware of a few collaborative projects borne from these discussions. 
For example, the collaboration between Jean-Daniel Fekete and Tim Kraska (Brown University) resulted in a recent TVCG paper~\cite{zgraggen2016progressive}.
